The 2014 SMT Competition

### 2015-08-03 2014/report/SMTCOMP.tex
tools -> competitions

Competitions among tools for a specific purpose are now common. Indeed SMT-COMP participated among dozen or so tools in the
FLoC Olympic Games in 2014~\cite{FLoC2014}. The competitions differ, of course, in their target problem set, but also differ in
their overall goals, scoring policies, and organization.

>>>>

Competitions among tools for a specific purpose are now common. Indeed SMT-COMP participated among a dozen or so competitions in the FLoC Olympic Games in 2014~\cite{FLoC2014}.  The competitions differ, of course, in their target problem set, but also in their overall goals, scoring policies, and organization.
